A Triple Origin for Twin Blue Stragglers in Close Binaries

### 2019-03-04 BSS7782.tex
after referee report

We propose a formation mechanism for twin blue stragglers (BSs) in
compact binaries that involves mass transfer from an evolved outer
tertiary companion on to the inner binary via a circumbinary disk.  We
apply this scenario to the observed double BS binary WOCS 7782 in the
old open cluster NGC 188, and show that its observed properties
\textbf{can be} reproduced within the context of the proposed model.
Based on this model, we predict the following properties for twin BSs:
(1) For the outer tertiary orbit, the initial orbital period should
lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days,
assuming initial masses for the inner binary components of $m_{\rm 1}
= 1.1$ M$_{\odot}$ and $m_{\rm 2} =$ 0.9 M$_{\odot}$ and an outer
tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  \textbf{(2)} After
Roche-lobe overflow, the outer star turns into a white dwarf (WD) of
mass 0.43 to 0.54\,\MSun. There is a correlation between the mass of
this WD and the outer orbital period: more massive WDs will be on
wider orbits.  (3) The rotational axes of both BSs will be aligned
with each other and the orbital plane of the outer tertiary WD. (4)
The BSs will have roughly equal masses, independent of their initial
masses (since the lower mass star accretes the most).  The dominant
accretor should, therefore, be enriched more effectively by the
accreted material.  As a result, one of the BSs will appear to be more
enriched by either He, C and O or by s-process elements, depending on
if the donor started to overflow its Roche lobe on, respectively, the
red giant or {\bf early} asymptotic giant branch.  (5) Relative to old
dense clusters with high-velocity dispersions, twin BSs in close
binaries formed from the proposed mechanism should be more frequent in
the Galactic field and younger open clusters with ages $\lesssim$ 4-6
Gyr, since then the donor will have a radiative envelope. (6) the
orbit of the binary BS will have a small semi-major axis (typically
$\aplt 0.3$\,au) and be close to circular ($e \aplt 0.2$).

@@

Even more curious, there exists in the old OC NGC 188 a
double BS binary, called WOCS 7782 \citep{geller08}.  The BS
population in NGC 188 has a bi-modal period-eccentricity distribution.
As discussed in \citet{2011MNRAS.410.2370L}, this could be hinting at
a triple origin for at least some subset of the total BS population.
As for WOCS 7782, \citet{2009Natur.462.1032M} observed a compact and
mildly eccentric (i.e., $e \sim 0.1$) binary star system with an
orbital period of $\sim$ 10 days hosting two roughly equal-mass BSs.  During a given binary-binary interaction, the probability
that not one but two direct (MS-MS) collisions will occur is less than
$10^{-2}$
\citep{1989AJ.....98..217L,2011MNRAS.410.2370L,2012MNRAS.425.2369L}.
Plus, binaries with collision products typically have relatively long
orbital periods \cite{2011Sci...334.1380F}. Dynamically, it is
difficult to form a short-period binary composed of two collision
products during a collisional interaction in a star cluster
\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}, \textit{and the timescale for exchanging another BS into a pre-existing BS-MS or BS-WD binary is much longer than the expected BS lifetime (see \citet{2011MNRAS.410.2370L} and the end of Section~\ref{sect:dyn} below)}.  So, how did WOCS 7782 form?

@@

Figure~\ref{fig:fig2} shows the parameter space in the P$_{\rm
  out}$-P$_{\rm in}$-plane for WOCS 7782.  \textbf{Here we adopted,
  for clarity,} initial component masses of $m_{\rm 1} = 1.1$ M$_{\rm
  \odot}$ and $m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary
components, and $m_{\rm 3} = 1.4 $M$_{\rm \odot}$ for the outer
tertiary.  \textbf{The scenario worked out is general, but we opt for
  these specific parameters because they appear to naturally result in
  a system with parameters similar to WOCS 7782.}  We compare the
circularization radius to the semi-major axis of the inner binary, for
which we require $a_{\rm c} > a_{\rm in}$, after folding in all
constraints from the requirements for dynamical stability (listed in
the caption of figure~\ref{fig:fig2}), and the assumption of an outer
tertiary that is Roche lobe-filling \textbf{(see
  \citet{2014MNRAS.438.1909D} for more details)}.
%\simon{Why do you consider it important to mention that the orbit is hard, and for what environment did you consider this? - NL: Deleted.}  
Note that the range of
plotted orbital periods P$_{\rm in}$ corresponding to a contact state
for the inner binary lies outside the range of plotted values for
$P_{\rm in}$ (for components with radii of 1 R$_{\odot}$),
since it does not contribute to constraining the outer orbital
properties.  The thick horizontal solid red line shows the allowed
range of outer semi-major axes, after folding in all of 
the aforementioned criteria.  These constraints result in a rather narrow
range of initial conditions for the outer orbit, namely 2.2 $\times$
10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days, \textit{which also directly translates into constraints on the final outer tertiary orbit.}
%, for
%which the tertiary star overfills its Roche lobe, the triple is (at
%least initially) dynamically stable and the accretion stream forms a
%gaseous ring around the inner binary.

\textbf{Finally, we compute the timescales for our hypothesized triple to undergo a direct interaction with another single or binary star.  Using the same assumptions for the host cluster properties of NGC 188 outlined in Section 3.2 of \citet{2011MNRAS.410.2370L} (right-hand column), we find upon setting the single-triple (1+3) and binary-triple (2+3) timescales equal to the expected duration of the mass transfer phase (i.e., $\sim$ 1 Myr) critical outer orbital periods for triples of, respectively, 8.1 $\times$ 10$^8$ and 2.4 $\times$ 10$^9$ days.  These critical outer tertiary orbital periods, which correspond to the times for a \textit{specific} triple to undergo an interaction, correspond to 1+3 and 2+3 interaction times that are much longer than the maximum predicted outer orbital period of the hypothesized white dwarf tertiary in our scenario.  Hence, we do not expect the mass transfer process to be interrupted by either 1+3 and 2+3 interactions.}

@@

With the adopted parameters, we can also estimate the final orbital
period of the left-over core from the tertiary star after mass
transfer.  The change in orbital separation due to non-conservative
mass transfer can be expressed in terms of the mass of the outer star
before and after mass transfer, i.e. $m_3$ and $m'_3$ respectively,
the total mass in the inner binary before ($m_{\rm in}$) and after
accretion ($m'_{\rm in}$) and the amount of angular momentum lost per
unit mass $\eta \simeq 3$.  {\bf The value of $\eta = 3$ was derived
  in \cite{1991A&A...241..419P,1995A&A...296..691P} by matching the
  orbital evolution and birthrate of Be-type x-ray binaries that
  experience non-considervative mass transfer. This value of
  consistent with the analysis for non-conservative evolution of type
  B mass transfer in \cite{2011A&A...527A..84K} and further
  constrained in \cite{2007ASPC..367..387P} to understand the mass
  transfer in the 100-day orbital period binary V379 Cep.}  Adopting
the relation between the orbital separation before mass transfer ($a$)
and after mass transfer ($a'$) from \cite{1995A&A...296..691P}
\begin{equation}
  {a' \over a} = \left( {m_3 m_{\rm in} \over m'_3 m'_{\rm in}} \right)^{-2}
  \left( {m_3 + m_{\rm in} \over m'_3 + m'_{\rm in}} \right)^{2\eta + 1},
\end{equation}
we arrive at the top brown curve in
figure\,\ref{fig:tertiarymass_vs_size}. This curve provides a prediction for 
the current orbital separation of the WD around the twin
BS 7782.
%% Tidal effects during mass \textbf{transfer}
%% have probably circularized the orbit, although some slight eccentricity
%% due to turbulent motion in the outer layers of the donor star may have
%% induced a small $e \ll 0.1$ eccentricity.

@@

We adopt initial masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$ and
$m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary components, and
between $m_{\rm 3} = 1.2$ and $m_{\rm 3} = 1.4$ M$_{\rm \odot}$ for
the tertiary star.  We evolve the tertiary star using the MESA
stellar-evolution code \cite{2011ApJS..192....3P} to a radius of about
100\,\RSun\, and 150\,\RSun, at which point we assume it to overfill
it's Roche lobe (see red \textbf{squares} in
figure~\ref{fig:tertiarymass_vs_size}).  We perform calculations for an
inner orbital separation of $a_{\rm in} = 0.10$\,au, $a_{\rm in} =
0.15$\,au and $a_{\rm in} = 0.20$\,au.  In total we performed 12
calculations at a resolution of 40k SPH particles and 12 at 80k.

@@

It is apparent that the mass transfer in the adopted triples leads to
a rather untidy evolution, since much of the donor mass is lost
through the second Lagrangian point to the right side of the donor
star in figure~\ref{fig:topview_at_t1000day}. A considerable amount of
mass is also lost through the third Lagrangian point (to the left of
the inner binary), although it is hard to actually \textbf{quantify the amount
of material lost}, becuase an appreciable fraction is expected to rain
back onto the triple system.  One remaining question is how much mass
is eventually ejected altogether from the triple system and is
therefore not accreted to any of the two inner stars. This value is
hard to estimate from the simulations, but an accretion efficiency of
$\apgt 0.6$ is necessary to make the scenario feasible. Over the time
scale for which we performed the calculations, this efficiency is
reached, but it is not clear how the system responds at later stages.

@@

The evolution of the inner orbit presented for several simulations in
figure~\ref{fig:mass_vs_semimajor_axis} is complicated.  This is
caused by the complex transport of mass, energy and angular momentum
through the accretion stream and throughout the system.  It is
therefore hard to quantify distinct trends in the evolution of the
triple system. In simulations of the response of an inner binary on
accretion from a circumbinary disk, \cite{2018arXiv181208175M}
conclude that the complexity of angular momentum transport between the
outer star and the accretion stream onto the individual inner stars,
is complicated and without clear trends. For most of our calculations
we agree with this statement, but in
figure~\,\ref{fig:mass_vs_semimajor_axis} we nevertheless present the
results of 6 of our calculations, three for a 1.2\,\MSun\, donor star
and three for a 1.4\,\MSun\, donor. The various coloured curves give
the resulting evolution of the inner orbit as a function of the total
mass in the inner binary. As the inner two stars accrete, the orbit
shrinks for a 1.2\,\MSun\, donor. These systems are expected to result
in a contact binary, that eventually may merge to form a single BS
with a mass more than twice the turn off. The required evolution in
order to explain the observed twin BS 7782 is indicated by the three
black curves; the simulated path clearly deviates from these. We,
therefore, argue that a 1.2\,\MSun\, donor has difficulty explaining
the observed orbital separation of $\sim 0.13$\,au in BSS 7782.

@@

\item As a consequence of the above, the initially lower mass MS star
  should accrete the most, and therefore be more enriched by accreted
  material.  This could be observable in the surface layers of a
  radiative star.  If the donor is an RGB star, the accretors will be
  enriched in mostly carbon, oxygen and helium, but if the donor is an
  AGB star the enrichment will be mostly in s-process elements.
  \textbf{Note that part of the mass liberated from the triple system
    through the second and third Lagrangian points may eventually be
    accreted back onto the system.  This could also have interesting
    consequences for the enrichment of the low-mass white dwarf.  Such
    a debris disk was recently found around the white dwarf SDSS
    J122859.93+104032.9 \cite{Manseretal2019}.
  }

@@

With an original outer star of mass $\sim 1.4$\,\MSun, the inner orbit
tends to expand. This eventually leads to a dynamically unstable
system resulting either in a collision or in the ejection of
(probably) the lowest mass star. This evolution could result in a
single ejected BS, with the other BS left in a relatively close and
eccentric orbit with a WD (the left-over core of the tertiary star).
These ``imposter'' BS-WD binaries would in principle mimic what is
expected theoretically for BSs formed from mass transfer in binary
stars. If such a dynamical instability engages relatively late in the
mass-tranfer phase, the white dwarf (maybe with a little left-over
envelope) is expected to be ejected. This would lead to a relatively
wide twin blue-straggler binary and a single low-mass white dwarf.

>>>>

We propose a formation mechanism for twin blue stragglers (BSs) in
compact binaries that involves mass transfer from an evolved outer
tertiary companion on to the inner binary via a circumbinary disk.  We
apply this scenario to the observed double BS binary WOCS 7782 in the
old open cluster NGC 188, and show that its observed properties
\textbf{can be} reproduced within the context of the proposed model.
Based on this model, we predict the following properties for twin BSs:
(1) For the outer tertiary orbit, the initial orbital period should
lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days,
assuming initial masses for the inner binary components of $m_{\rm 1}
= 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.7$ to $0.9$M$_{\odot}$ and an
outer tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  \textbf{(2)}
After Roche-lobe overflow, the outer star turns into a white dwarf
(WD) of mass 0.43 to 0.54\,\MSun. There is a correlation between the
mass of this WD and the outer orbital period: more massive WDs will be
on wider orbits.  (3) The rotational axes of both BSs will be aligned
with each other and the orbital plane of the outer tertiary WD. (4)
The BSs will have roughly equal masses, independent of their initial
masses (since the lower mass star accretes the most).  The dominant
accretor should, therefore, be enriched more effectively by the
accreted material.  As a result, one of the BSs will appear to be more
enriched by either He, C and O or by s-process elements, depending on
whether the donor started to overflow its Roche lobe on, respectively,
the red giant or {\bf early} asymptotic giant branch.  (5) Relative to
old dense clusters with high-velocity dispersions, twin BSs in close
binaries formed from the proposed mechanism should be more frequent in
the Galactic field and younger open clusters with ages $\lesssim$ 4-6
Gyr, since then the donor will have a radiative envelope. (6) the
orbit of the binary BS will have a small semi-major axis (typically
$\aplt 0.3$\,au) and be close to circular ($e \aplt 0.1$).

@@

Even more curious, there exists in the old OC NGC 188 a double BS
binary, called WOCS 7782 \citep{2009AJ....137.3743G}.  The BS
population in NGC 188 has a bi-modal period-eccentricity distribution.
As discussed in \citet{2011MNRAS.410.2370L}, this could be hinting at
a triple origin for at least some subset of the total BS population.
As for WOCS 7782, \citet{2009Natur.462.1032M} observed a compact and
mildly eccentric (i.e., $e \sim 0.1$) binary star system with an
orbital period of $\sim$ 10 days hosting two roughly equal-mass BSs.
During a given binary-binary interaction, the probability that not one
but two direct (MS-MS) collisions will occur is less than $10^{-2}$
\citep{1989AJ.....98..217L,2011MNRAS.410.2370L,2012MNRAS.425.2369L}.
Plus, binaries with collision products typically have relatively long
orbital periods \citep{2011Sci...334.1380F}. Dynamically, it is
difficult to form a short-period binary composed of two collision
products during a collisional interaction in a star cluster
\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}, \textbf{and the
  timescale for exchanging another BS into a pre-existing BS-MS or
  BS-WD binary is much longer than the expected BS lifetime (see
  \citet{2011MNRAS.410.2370L} and the end of Section~\ref{sect:dyn}
  below)}.  So, how did WOCS 7782 form?

@@

Figure~\ref{fig:fig2} shows the parameter space in the P$_{\rm
  out}$-P$_{\rm in}$-plane for WOCS 7782.  \textbf{Here we adopted,
  for clarity,} initial component masses of $m_{\rm 1} = 1.1$ M$_{\rm
  \odot}$ and $m_{\rm 2} = 0.9$ M$_{\rm \odot}$ for the inner binary
components, and $m_{\rm 3} = 1.4 $M$_{\rm \odot}$ for the outer
tertiary.  \textbf{The scenario worked out is general, but we opt for
  these specific parameters because they appear to naturally result in
  a system with parameters similar to WOCS 7782.}  We compare the
circularization radius to the semi-major axis of the inner binary, for
which we require $a_{\rm c} > a_{\rm in}$, after folding in all
constraints from the requirements for dynamical stability (listed in
the caption of figure~\ref{fig:fig2}), and the assumption of an outer
tertiary that is Roche lobe-filling \textbf{(see
  \citet{2014MNRAS.438.1909D} for more details)}.
%\simon{Why do you consider it important to mention that the orbit is hard, and for what environment did you consider this? - NL: Deleted.}  
Note that the range of plotted orbital periods P$_{\rm in}$
corresponding to a contact state for the inner binary lies outside the
range of plotted values for $P_{\rm in}$ (for components with radii of
1 R$_{\odot}$), since it does not contribute to constraining the outer
orbital properties.  The thick horizontal solid red line shows the
allowed range of outer semi-major axes, after folding in all of the
aforementioned criteria.  These constraints result in a rather narrow
range of initial conditions for the outer orbit, namely 2.2 $\times$
10$^{2}$ days $\le$ P$_{\rm out}$ $\le$ 1.1 $\times$ 10$^3$ days,
\textbf{which also directly translates into constraints on the final
  outer tertiary orbit.}
%, for
%which the tertiary star overfills its Roche lobe, the triple is (at
%least initially) dynamically stable and the accretion stream forms a
%gaseous ring around the inner binary.

\textbf{Finally, we compute the timescales for our hypothesized triple
  to undergo a direct interaction with another single or binary star.
  Using the same assumptions for the host cluster properties of NGC
  188 outlined in Section 3.2 of \citet{2011MNRAS.410.2370L}
  (right-hand column), we find upon setting the single-triple (3+1)
  and binary-triple (3+2) timescales equal to the expected duration of
  the mass transfer phase (i.e., $\sim 1$\, Myr) critical outer
  orbital periods for triples for $\gg 1$\,Myr.  These critical outer
  tertiary orbital periods, which correspond to the times for a
  specific triple to undergo an interaction, correspond to 3+1 and 3+2
  interaction times that are much longer than the maximum predicted
  outer orbital period of the hypothesized white dwarf tertiary in our
  scenario.  We therefore do not expect the mass transfer process to
  be interrupted by a dynamical interaction in the cluster center.}

@@

With the adopted parameters, we can also estimate the final orbital
period of the left-over core from the tertiary star after mass
transfer.  The change in orbital separation due to non-conservative
mass transfer can be expressed in terms of the mass of the outer star
before and after mass transfer, i.e. $m_3$ and $m'_3$ respectively,
the total mass in the inner binary before ($m_{\rm in}$) and after
accretion ($m'_{\rm in}$) and the amount of angular momentum lost per
unit mass $\eta \simeq 3$.  {\bf The value of $\eta = 3$ was derived
  in \cite{1991A&A...241..419P,1995A&A...296..691P} by matching the
  orbital evolution and birthrate of Be-type x-ray binaries that
  experience non-considervative mass transfer. This value of
  consistent with the analysis for non-conservative evolution of type
  B mass transfer in \cite{2011A&A...527A..84K} and further
  constrained in \cite{2007ASPC..367..387P} to understand the mass
  transfer in the 100-day orbital period binary V379 Cep.}  Adopting
the relation between the orbital separation before mass transfer ($a$)
and after mass transfer ($a'$) from \cite{1995A&A...296..691P}
\begin{equation}
  {a' \over a} = \left( {m_3 m_{\rm in} \over m'_3 m'_{\rm in}} \right)^{-2}
  \left( {m_3 + m_{\rm in} \over m'_3 + m'_{\rm in}} \right)^{2\eta + 1},
\end{equation}
we arrive at the top red curve in
figure\,\ref{fig:tertiarymass_vs_size}. This curve provides a prediction for 
the current orbital separation of the WD around the twin
BS 7782.
%% Tidal effects during mass \textbf{transfer}
%% have probably circularized the orbit, although some slight eccentricity
%% due to turbulent motion in the outer layers of the donor star may have
%% induced a small $e \ll 0.1$ eccentricity.

@@

We adopt initial masses of $m_{\rm 1} = 1.1$ M$_{\rm \odot}$ and
$m_{\rm 2} = 0.7$ M$_{\rm \odot}$ or 0.9\,M$_{\rm \odot}$ for the
inner binary components, and between $m_{\rm 3} = 1.2$ and $m_{\rm 3}
= 1.4$ M$_{\rm \odot}$ for the tertiary star.  We evolve the tertiary
star using the MESA stellar-evolution code \cite{2011ApJS..192....3P}
to a radius of about 100\,\RSun\, and 150\,\RSun, at which point we
assume it to overfill it's Roche lobe (see red \textbf{squares} in
figure~\ref{fig:tertiarymass_vs_size}).  We perform calculations for
an inner orbital separation of $a_{\rm in} = 0.10$\,au, $a_{\rm in} =
0.15$\,au and $a_{\rm in} = 0.20$\,au.  In total we performed 12
calculations at a resolution of 40k SPH particles and 12 at 80k.

@@

It is apparent that the mass transfer in the adopted triples leads to
a rather untidy evolution, since much of the donor mass is lost
through the second Lagrangian point to the right side of the donor
star in figure~\ref{fig:topview_at_t1000day}. A considerable amount of
mass is also lost through the third Lagrangian point (to the left of
the inner binary), although it is hard to actually \textbf{quantify
  the amount of material lost}, becuase an appreciable fraction may to
rain back onto the triple system.  One remaining question is how much
mass is eventually ejected altogether from the triple system and is
therefore not accreted to any of the two inner stars. This value is
hard to estimate from the simulations, but an accretion efficiency of
$\apgt 0.8$ is necessary to make the scenario feasible. Over the time
scale for which we performed the calculations, this efficiency is
reached, but it is not clear how the system responds at later stages.

@@

The evolution of the inner orbit presented for several simulations in
figure~\ref{fig:mass_vs_semimajor_axis} is complicated.  This is
caused by the complex transport of mass, energy and angular momentum
through the accretion stream and throughout the system.  It is
therefore hard to quantify distinct trends in the evolution of the
triple system. In simulations of the response of an inner binary on
accretion from a circumbinary disk, \cite{2018arXiv181208175M}
conclude that the complexity of angular momentum transport between the
outer star and the accretion stream onto the individual inner stars,
is complicated and without clear trends. For most of our calculations
we agree with this statement, but in
figure~\,\ref{fig:mass_vs_semimajor_axis} we nevertheless present the
results of 6 of our calculations, three for a 1.2\,\MSun\, donor star
and three for a 1.4\,\MSun\, donor. The various coloured curves give
the resulting evolution of the inner orbit as a function of the total
mass in the inner binary. As the inner two stars accrete, the orbit
shrinks for a 1.2\,\MSun\, donor. These systems are expected to result
in a contact binary, that eventually may merge to form a single BS
with a mass more than twice the turn off in orbit around a low-mass
white dwarf. The required evolution in order to explain the observed
twin BS 7782 is indicated by the three black curves; the simulated
path clearly deviates from these. We, therefore, argue that a
1.2\,\MSun\, donor has difficulty explaining the observed orbital
separation of $\sim 0.13$\,au in BSS 7782.

@@

  \textbf{ We further validated this statement by performing an
    additional series of calculations in which we vary the mass of the
    tertiary star in the initial triple from 0.5\,\MSun\, to
    0.7\,\MSun\, and 0.9\,\MSun. In
    fig.\,\ref{fig:mass_ratio_evolution_for_14MSun} we present the
    evolution of the normalized mass ratio in these binaries. with
    these calculations we demonstrate that a low-mass ratio initially
    tends to evolve towards an equal mass ratio.  }

  \begin{figure}[ht!]
  \includegraphics[width=\columnwidth]{fig_mass_ratio_evolution_for_14MSun.pdf}
  \caption{Evolution of the mass ratio for initial triples with an
    inner orbital separation of 0.1\,au (orange dotted curve) and
    0.2\,au (all other curves). The initial primary mass was
    1.4\,\MSun\, overfilling it's Roche lobe at a radius of
    100\,\RSun. the companion masses are $m_2= 0.9$\,\MSun\, and the
    mass of the tertiary is indicated in the legend. The dotted black
    line indicates the required mass-ratio evolution in order to
    eventually reach an equal mass-ratio blue-straggler binary.
\label{fig:mass_ratio_evolution_for_14MSun}}
\end{figure}

\item As a consequence of the above, the initially lower mass MS star
  should accrete the most, and therefore be more enriched by accreted
  material.  This could be observable in the surface layers of a
  radiative star.  If the donor is an RGB star, the accretors will be
  enriched in mostly carbon, oxygen and helium, but if the donor is an
  AGB star the enrichment will be mostly in s-process elements.
  \textbf{Note that part of the mass liberated from the triple system
    through the second and third Lagrangian points may eventually be
    accreted back onto the system.  This could also have interesting
    consequences for the enrichment of the low-mass white dwarf.  Such
    a debris disk was recently found around the white dwarf SDSS
    J122859.93+104032.9 \citep{Manseretal2019}.  }

@@

With an original outer star of mass $\sim 1.4$\,\MSun, the inner orbit
tends to expand. This eventually leads to a dynamically unstable
system resulting either in a collision or in the ejection of
(probably) the lowest mass star. This evolution could result in a
single ejected BS, with the other BS left in a relatively close and
eccentric orbit with a WD (the left-over core of the tertiary star).
Such a close BS-WD binary would be hard to explain in another way.
%% These ``imposter'' BS-WD binaries would in principle mimic what is
%% expected theoretically for BSs formed from mass transfer in binary
%% stars.
If such a dynamical instability engages relatively late in the
mass-tranfer phase, the white dwarf (maybe with a little left-over
envelope) is expected to be ejected. This would lead to a relatively
wide twin blue-straggler binary and a single low-mass white dwarf.
